### 2024-08-28 manuscripts/06-labour-v5/manuscript_main.tex
....

@@

\subsection*{Children of the four parental types}

@@

\subsection*{Synthetic parents}

@@

\subsection*{Estimating the effect of having a Hispanic last name}

@@

\subsection*{Estimating the effect of identifying as Hispanic}

@@

\subsection*{Threats to Identification}

@@

\section*{From the Data: The Differences Between HW and WH Couples}\label{sec:hw-wh-couples-data}

@@

\subsection*{The Effect of Having a Hispanic Last Name on Educational Outcomes}

@@

However, there is a notable difference when it comes to higher education outcomes. HW children are 2 percentage points less likely to earn an associate degree and 3 percentage points less likely to earn a bachelor's degree compared to their WH peers. These gaps are slightly larger for HW women, who are 3 percentage points less likely to earn an associate degree and 4 percentage points less likely to earn a bachelor's degree. For HW men, the gap is 2 percentage points for an associate degree and statistically insignificant for a bachelor's degree.

These results suggest that while the overall educational attainment gap between HW and WH children is small in terms of years of education, the disparities become more pronounced when considering higher education milestones, particularly for HW women. However, given the fact that HWs have ,more educated mothers than WHs, we would expect them to have higher levels of educational attainment \autocite{kimball2009risk, gould2020does}. This could indicate potential barriers or discrimination in access to higher education for HW children, particularly.

\subsection*{The Effect of Having a Hispanic Last Name and Hispanic Identity on Labor Market Outcomes}

>>>>

\section{Introduction}

@@

\subsection{Children of the four parental types}

@@

\subsection{Synthetic parents}

@@

\subsection{Estimating the effect of having a Hispanic last name}

@@

\subsection{Estimating the effect of identifying as Hispanic}

@@

\subsection{Threats to Identification}

@@

\section{From the Data: The Differences Between HW and WH Couples}\label{sec:hw-wh-couples-data}

@@

\subsection{The Effect of Having a Hispanic Last Name on Educational Outcomes}

@@

However, there is a notable difference when it comes to higher education outcomes. HW children are 2 percentage points less likely to earn an associate degree and 3 percentage points less likely to earn a bachelor's degree compared to their WH peers. HW children are 2 percentage points less likely to earn an associate degree compared to their WH peers, representing a 13.3\% reduction relative to the WH associate degree rate of 15\%. HW children are 3 percentage points less likely to earn a bachelor's degree compared to their WH peers, which is a 13\% reduction relative to the WH bachelor's degree rate of 23\%. These gaps are slightly larger for HW women, who are 3 percentage points less likely to earn an associate degree and 4 percentage points less likely to earn a bachelor's degree. For HW men, the gap is 2 percentage points for an associate degree and statistically insignificant for a bachelor's degree.

These results suggest that while the overall educational attainment gap between HW and WH children is small in terms of years of education, the disparities become more pronounced when considering higher education milestones, particularly for HW women. However, given the fact that HWs have more educated mothers than WHs, we would expect them to have higher levels of educational attainment \autocite{kimball2009risk, gould2020does}. This could indicate potential barriers or discrimination in access to higher education for HW children, particularly.

\subsection{The Effect of Having a Hispanic Last Name and Hispanic Identity on Labor Market Outcomes}

### 2024-08-28 manuscripts/06-labour-v5/tab08-regression-weekearn-mex.tex
....

\begin{table}[H]

\caption{Effect of Having Hispanic Last Name: Hispanics with Mexican Ancestry  \label{tab:lastnamereg-weekearm-mex}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Log weekly \\ earnings} & \specialcell{(2) \\ Log weekly \\ earnings} & \specialcell{(3) \\  Log weekly \\ earnings} & \specialcell{(4) \\  Log weekly \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.01} & \num{-0.03}* & \num{0.00} & \num{-0.01}\\
 & (\num{0.02}) & (\num{0.02}) & (\num{0.01}) & (\num{0.01})\\
Constant & \num{6.53}*** &  &  & \\
 & (\num{0.04}) &  &  & \\
\midrule
\textit{Controlling for:} &  &  &  & \\
State FE &  & X & X & X\\
Year FE &  & X & X & X\\
Age FE &  & X & X & X\\
Education FE &  &  & X & X\\
Parental Background &  &  &  & X\\
Observations & \num{4535} & \num{4535} & \num{4535} & \num{4535}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}) where the dependent variable is log weekly earnings.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name: Hispanics with Mexican Ancestry  \label{tab:lastnamereg-weekearm-mex}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Log weekly \\ earnings} & \specialcell{(2) \\ Log weekly \\ earnings} & \specialcell{(3) \\  Log weekly \\ earnings} & \specialcell{(4) \\  Log weekly \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.01} & \num{-0.04}** & \num{-0.01} & \num{-0.01}\\
 & (\num{0.02}) & (\num{0.02}) & (\num{0.01}) & (\num{0.02})\\
Constant & \num{6.53}*** &  &  & \\
 & (\num{0.04}) &  &  & \\
\midrule
\textit{Controlling for:} &  &  &  & \\
State FE &  & X & X & X\\
Year FE &  & X & X & X\\
State-Year FE &  & X & X & X\\
Age &  & X & X & X\\
Education &  &  & X & X\\
Parental Background &  &  &  & X\\
Observations & \num{4515} & \num{4515} & \num{4515} & \num{4515}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}) where the dependent variable is log weekly earnings.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2024-08-28 manuscripts/07-economic-letters-v5/Hadah-Hispanic-Last-Names.tex
....

\begin{abstract}
\singlespacing % Set single spacing for the abstract
Do individuals with Hispanic names face labor market discrimination? This study analyzes the impact of Hispanic-sounding surnames on wages among inter-ethnic children with one White and one Hispanic parent. I find that individuals with Hispanic surnames often earn less, with a notable wage gap favoring those with White surnames. People born to Hispanic fathers and White mothers receive 0.3 years of education less than those born to White fathers and Hispanic mothers. Males born to Hispanic fathers and White mothers earn 5 percentage points less than those born to White fathers and Hispanic mothers, largely due to educational differences. Additionally, men with Spanish-sounding last names who identify as Hispanic earn significantly less, again due to educational disparities.
\end{abstract}

@@

A large literature documents substantial earnings gaps across race and ethnicity \citep{bayer2018divergent, charles2008prejudice, card1992school, fryer2004causes, rubinstein2014pride, bertrand2004emily, juhn1991accounting}. Hispanics constitute a large and growing portion of the population in the United States. As the number of Hispanics increases, determining whether ethnic discrimination affects their labor market outcomes becomes increasingly crucial \citep{chettyUnitedStatesStill2014, chettyEffectsExposureBetter2016,chettyFadingAmericanDream2017,abramitzkyImmigrantsAssimilateMore2020a, abramitzkyNationImmigrantsAssimilation2014,abramitzkyCulturalAssimilationAge2016,chettyWhereLandOpportunity2014}. Thus, it is important to understand whether a person's ethnicity affects their labor market outcomes. Assimilation and mobility are crucial because they reflect how well Hispanics can integrate into society and move up the socioeconomic ladder.

In this paper, I answer the following question. Does having a Hispanic last name affect education and labor market outcomes? Moreover, I aim to show that comparing Hispanic Whites to non-Hispanic Whites might create an artificially higher earnings gap since the two groups differ on many observable characteristics. \footnote{Observable characteristics refer to factors that can be measured and quantified, such as education level, work experience, and immigration status.} Others have attempted to compare how native-born White Hispanics fare to non-Hispanic Whites and foreign-born Hispanics. In \citet{antman2020ethnic,antmanEthnicAttritionObserved2016,antmanEthnicAttritionObserved2016a,antmanEthnicAttritionAssimilation2020}, the authors compare the health and educational outcomes of Hispanic Whites to non-Hispanic Whites and native-born Hispanics to foreign-born Hispanics. They find gaps in education and health between Hispanics and Whites. They also find that native-born Hispanics are more likely than their foreign-born counterparts to report poor health. \citet{davilaChangesRelativeEarnings2008} documents many gaps in labor market outcomes between Hispanics and Whites. They attribute a big part of this gap to differences in education, experience, immigration status, and regional differences.

The US population is growing in diversity. The proportion of non-Whites has increased by more than 10 percentage points from 13 percent in 1995 to 23 percent in 2019. The number of Hispanics has grown by 9 percentage points from 9 percent in 1995 to 16 percent in 2019.\footnote{The portion of non-Whites and Hispanics is calculated using the Current Population Survey (CPS).} Native-born White Hispanic men earn 21\% less than White men, although a substantial portion of the earnings gap is due to educational differences between Hispanics and Whites \citep{duncan2006hispanics, duncan2018identifying, duncan2018socioeconomic}. Some of the earnings differences may also be due to discrimination which will have negative consequences. For example, discrimination against Hispanics can lead to reduced job opportunities, lower wages, and hinder assimilation. In this paper, I examine the role of having a Hispanic last name on labor market and educational outcomes outcomes.

Identifying discrimination is difficult because of factors that affect labor market outcomes that are unobservable to economists---such as unobserved skills and separating it from prejudice and stereotypes. One strategy used by researchers is audit or resume studies. \citet{bertrand2004emily} conducted an audit study where identical resumes were sent to employers with White and Black-sounding names. This approach, however, has its drawbacks. Audit studies only observe callbacks, not wages.

@@

@@

The CPS sample is restricted to White, US-born citizens aged 25-40, born between 1960-2000. Parents are classified as Hispanic if born in a Spanish-speaking country or Puerto Rico, and White if US-born. Four parental types are identified: (1) White father and White mother (WW), (2) White father and Hispanic mother (WH), (3) Hispanic father and White mother (HW), and (4) Hispanic father and Hispanic mother (HH).

@@

The difference in means between Hispanics and non-Hispanic Whites could result from discrimination. It can also be caused by differences in innate abilities, skills, and parental investments. While controlling for observable skill measures, I compare children of inter-ethnic marriages, HW and WH. WH and HW children are more similar in characteristics but provide employers, and the labor market, with different signals.\footnote{WH and HW children are both half White, half Hispanic.} WH children will have a non-Hispanic last name, while HW children will have a Hispanic last name. This is a method developed by \citet{rubinstein2014pride}.

@@

In this section I restrict the sample to WH and HW groups. Let $Y_{ist}$ be the outcome of interest for person $i$ in state $s$ at time $t$. $HW_{ist}$ is an indicator variables for the type of parents of person $i$ has. $X_{ist}$ is a vector of controls that includes age and numbers of hours worked, $\gamma_{st}$ are state-year fixed effects (FE), and $\phi_{ist}$ represents the error term. The equation for this strategy is written as follows:
\begin{equation} \label{eq:1a}
Y_{ist} = \beta_{1} HW_{ist} + X_{ist} \pi + \gamma_{st} + \phi_{ist}
\end{equation}

@@

A potential measurement error arises from using parents' birthplace in the CPS data as a proxy for ethnicity and last name. However, this concern is minimal as most Hispanics from 1960 to 2000 were first-generation immigrants. Census data shows only 3\% of native-born Americans identified as Hispanic, making it highly improbable for an inter-ethnic child to have a native-born, second-generation+ Hispanic father.\footnote{Self-reported Hispanic identity among first-generation Hispanic immigrants and native-borns are based on the author’s calculations from the 1960-2000 Census. The sample includes Whites, who are married, and are between the ages 25 and 40.} Empirical evidence from the CPS and US Census will be used to evaluate these concerns and support the validity of the identification strategy.

@@

In this section, I examine the data to validate my empirical strategy, focusing on educational and economic outcomes for four ethnic groupings—White White (WW), White Hispanic (WH), Hispanic White (HW), and Hispanic Hispanic (HH)—as shown in Table \ref{tab:combined-sum}. The data indicates marriage selection, with smaller differences between HW and WH children compared to the other groups, making them a more suitable comparison for analyzing labor market discrimination against Hispanics. Using the synthetic parents sample constructed from Census data, we observe that WW couples have the highest household education levels (24.95 years), while HH couples have the lowest (17.13 years). Inter-ethnic couples fall in between, with WH households totaling 22.68 years of schooling and HW households slightly behind at 21.50 years. Notably, HW wives are more educated than their WH peers, which could have implications for the educational attainment of HW children, as mothers play a crucial role in human capital accumulation.

@@

Analysis of White, U.S.-born Hispanics ages 25-40 (Table \ref{tab:lastname-ed-reg}) reveals that HW children receive 0.2 years less education than WH children. While there is no significant difference in high school dropout rates, HW children are 2 percentage points less likely to earn an associate degree and 3 percentage points less likely to earn a bachelor's degree. These gaps are larger for HW women in higher education. These disparities suggest potential barriers or discrimination in access to higher education for HW children, particularly women.

@@

Results from Table \ref{tab:lastnamereg} indicate a 1 percentage point employment gap between HW and WH workers, and a 5 percentage point crude earnings gap. However, when controlling for education, the earnings gap reduces to a statistically insignificant 1 percentage point.

@@

This study examines discrimination against Hispanics in the U.S. labor market, focusing on the impact of Hispanic last names and identification on education and earnings. The research finds that inter-ethnic individuals with Spanish-sounding last names receive 0.2 years less education and are more likely to be unemployed. HW children earn 5 percentage points less than WH children, but this gap becomes statistically insignificant when controlling for education.

These results align with existing literature on disparities in educational access \citep{bergman2018education,gaddis2024racial}. While the earnings gap diminishes when controlling for education, this doesn't necessarily indicate an absence of discrimination, as education itself can be influenced by bias.

Further research is needed to comprehensively understand the earnings gaps between Hispanics and Whites, particularly considering that mothers of HW children have higher education and earnings, which theoretically should lead to better outcomes for their children.

>>>>

\begin{abstract}
\singlespacing % Set single spacing for the abstract
Do individuals with Hispanic names face labor market discrimination? This study analyzes the impact of Hispanic-sounding surnames on wages among inter-ethnic children with one White and one Hispanic parent. I find that individuals with Hispanic surnames receive less education, more likely to be unemployed, and often earn less, with a notable wage gap favoring those with White surnames. People born to Hispanic fathers and White mothers receive 0.3 years of education less than those born to White fathers and Hispanic mothers. Males born to Hispanic fathers and White mothers are 1 percentage point more likely to be unemployed, and they also earn 5 percentage points less than those born to White fathers and Hispanic mothers. The earnings gap is largely due to educational differences.
\end{abstract}

@@

A large literature documents substantial earnings gaps across race and ethnicity \citep{bayer2018divergent, charles2008prejudice, card1992school, fryer2004causes, rubinstein2014pride, bertrand2004emily, juhn1991accounting}. Hispanics constitute a large and growing portion of the population in the United States. As the number of Hispanics increases, determining whether ethnic discrimination influences their labor market outcomes becomes increasingly crucial \citep{chettyUnitedStatesStill2014, chettyEffectsExposureBetter2016,chettyFadingAmericanDream2017,abramitzkyImmigrantsAssimilateMore2020a, abramitzkyNationImmigrantsAssimilation2014,abramitzkyCulturalAssimilationAge2016,chettyWhereLandOpportunity2014}. Thus, it is important to understand how a person's ethnicity affects their labor market outcomes. Assimilation and mobility are crucial because they reflect how well Hispanics can integrate into society and move up the socioeconomic ladder.

In this paper, I answer the following question: does having a Hispanic last name affect education and labor market outcomes? Moreover, I aim to show that comparing Hispanic Whites to non-Hispanic Whites might create an artificially higher earnings gap since the two groups differ on many observable characteristics. \footnote{Observable characteristics refer to factors that can be measured and quantified, such as education level, work experience, and immigration status.} Others have attempted to compare how native-born White Hispanics fare compared to non-Hispanic Whites and foreign-born Hispanics. In \citet{antman2020ethnic,antmanEthnicAttritionObserved2016,antmanEthnicAttritionObserved2016a,antmanEthnicAttritionAssimilation2020}, the authors compare the health and educational outcomes of Hispanic Whites to non-Hispanic Whites and native-born Hispanics to foreign-born Hispanics. They find gaps in education and health between Hispanics and Whites. They also find that native-born Hispanics are more likely than their foreign-born counterparts to report poor health. \citet{davilaChangesRelativeEarnings2008} documents many gaps in labor market outcomes between Hispanics and Whites. They attribute a big part of this gap to differences in education, experience, immigration status, and regional differences.

The US population is growing in diversity. The proportion of non-Whites has increased by more than 10 percentage points from 13 percent in 1995 to 23 percent in 2019. The number of Hispanics has grown by 9 percentage points from 9 percent in 1995 to 16 percent in 2019.\footnote{The portion of non-Whites and Hispanics is calculated using the Current Population Survey (CPS).} Native-born White Hispanic men earn 21\% less than White men, although a substantial portion of the earnings gap is due to educational differences between Hispanics and Whites \citep{duncan2006hispanics, duncan2018identifying, duncan2018socioeconomic}. Some of the earnings differences may also be due to discrimination which will have negative consequences. For example, discrimination against Hispanics can lead to reduced job opportunities, lower wages, and hinder assimilation. In this paper, I examine the role of having a Hispanic last name on labor market and educational outcomes.

Identifying discrimination is difficult due to factors affecting labor market outcomes that are unobservable to economists, such as unobserved skills, and the challenge of separating these factors from prejudice and stereotypes. One strategy used by researchers is audit or resume studies. \citet{bertrand2004emily} conducted an audit study where identical resumes were sent to employers with White and Black-sounding names. This approach, however, has its drawbacks. Audit studies only observe callbacks, not wages.

@@

I find that a person with a Hispanic last name receives less education, is more likely to be unemployed, and earns less. The results suggest that individuals with Hispanic last names receive 0.2 years less education and are more likely to be unemployed. The gap in education is equivalent to a 1.9\% reduction, and the unemployment gap is equal to a 14\% increase. The earnings gap between individuals with Hispanic last names and those with White last names is 5 percentage points. The earnings gap between individuals with Hispanic last names and those with White last names is 5 percentage points. However, when controlling for education, the earnings gap reduces to 1 percentage point. The results suggest that the earnings gap is largely due to differences in education.

@@

The CPS sample is restricted to White, U.S.-born citizens aged 25-40, born between 1960 and 2000. Parents are classified as Hispanic if born in a Spanish-speaking country or Puerto Rico, and White if they are US-born. Four parental types are identified: (1) White father and White mother (WW), (2) White father and Hispanic mother (WH), (3) Hispanic father and White mother (HW), and (4) Hispanic father and Hispanic mother (HH).

@@

The difference in means between Hispanics and non-Hispanic Whites could result from either discrimination or differences in innate abilities, skills, and parental investments. It can also be caused by differences in innate abilities, skills, and parental investments. While controlling for observable skill measures, I compare children of inter-ethnic marriages, HW and WH. WH and HW children are more similar in characteristics but provide employers, and the labor market, with different signals.\footnote{WH and HW children are both half White, half Hispanic.} WH children will have a non-Hispanic last name, while HW children will have a Hispanic last name. This is a method developed by \citet{rubinstein2014pride}.

@@

In this section I restrict the sample to WH and HW groups. Let $Y_{ist}$ be the outcome of interest for person $i$ in state $s$ at time $t$. $HW_{ist}$ is an indicator variable for the type of parents person $i$ has. $X_{ist}$ is a vector of controls that includes age and numbers of hours worked, $\gamma_{st}$ are state-year fixed effects (FE), and $\phi_{ist}$ represents the error term. The equation for this strategy is written as follows:
\begin{equation} \label{eq:1a}
Y_{ist} = \beta_{1} HW_{ist} + X_{ist} \pi + \gamma_{st} + \phi_{ist}
\end{equation}

@@

A potential measurement error arises from using parents' birthplace in the CPS data as a proxy for both ethnicity and last name. However, this concern is minimal as most Hispanics from 1960 to 2000 were first-generation immigrants. Census data shows only 3\% of native-born Americans identified as Hispanic, making it highly improbable for an inter-ethnic child to have a native-born, second-generation+ Hispanic father.\footnote{Self-reported Hispanic identity among first-generation Hispanic immigrants and native-borns are based on the author’s calculations from the 1960-2000 Census. The sample includes Whites, who are married, and are between the ages 25 and 40.} Empirical evidence from the CPS and US Census will be used to evaluate these concerns and support the validity of the identification strategy.

@@

In this section, I examine the data to validate my empirical strategy, focusing on educational and economic outcomes for four ethnic groupings—White White (WW), White Hispanic (WH), Hispanic White (HW), and Hispanic Hispanic (HH)—as shown in Table \ref{tab:combined-sum}. The data indicates marriage selection, with smaller differences between HW and WH children compared to the other groups. This similarity makes HW and WH children a more suitable comparison for analyzing labor market discrimination against Hispanics. Using the synthetic parents sample constructed from Census data, we observe that WW couples have the highest household education levels (24.95 years), while HH couples have the lowest (17.13 years). Inter-ethnic couples fall in between, with WH households totaling 22.68 years of schooling and HW households slightly behind at 21.50 years. Notably, HW wives are more educated than their WH peers, which could have implications for the educational attainment of HW children, as mothers play a crucial role in human capital accumulation \citep{kimball2009risk,magruder2010intergenerational}.

@@

Analysis of White, U.S.-born Hispanics ages 25-40 (Table \ref{tab:lastname-ed-reg}) reveals that HW children receive 0.2 years less education than WH children---that represents a 1.5\% reduction. While there is no significant difference in high school dropout rates, HW children are 2 percentage points less likely to earn an associate degree and 3 percentage points less likely to earn a bachelor's degree, which is equal to a 15\% reduction. These gaps are larger for HW women in higher education. These disparities suggest potential barriers or discrimination in access to higher education for HW children, particularly women.

@@

Results from Table \ref{tab:lastnamereg} indicate a 1 percentage point employment gap between HW and WH workers, and a 5 percentage point crude earnings gap. However, when controlling for education, the earnings gap reduces to a statistically insignificant 1 percentage point. I also find that HW children are 1 percentage point more likely to be unemployed than WH children. The gap in unemployment is equivalent to a 14\% increase and is statistically significant even after controlling for education. These results suggest that having a Hispanic last name negatively impacts labor market outcomes, particularly in terms of employment.

@@

This study examines discrimination against Hispanics in the U.S. labor market, focusing on the impact of Hispanic last names and identification on education and earnings. This research finds that inter-ethnic individuals with Spanish-sounding last names receive 0.2 years less education and are more likely to be unemployed. HW children earn 5 percentage points less than WH children, but this gap becomes statistically insignificant when controlling for education.

These results align with existing literature on disparities in educational access \citep{bergman2018education,gaddis2024racial}. While the earnings gap diminishes when controlling for education, this doesn't necessarily indicate an absence of discrimination, as education itself can be influenced by bias. Moreover, educational differences cannot explain the gaps in unemployment, suggesting that discrimination may play a role in labor market outcomes of individuals with Hispanic last names. Further research is needed to comprehensively understand the earnings gaps between Hispanics and Whites, particularly considering that mothers of HW children have higher education and earnings, which theoretically should lead to better outcomes for their children.
